Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-20 rates-neurips-21/rates.tex
mini edit in upper bound

\section{Upper bound: polyhedral surrogates}
In this section, we develop the proof of Theorem \ref{thm:main-upper}.
At a high level, the proof has two parts:
\begin{enumerate}
  \item Fix $p \in \simplex$.
        Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
  \item Apply this result to a finite subset $P$ of $\simplex$, namely the vertices of the level sets of $\Gamma$.
        Argue (carefully) that, because a general $p$ is a convex combination of vertices of its own level set, $R_{\ell}(\psi(u),p) \leq \left(\max_{p' \in P} \alpha_{p'}\right) R_L(u,p)$.
        This implies a linear conditional transfer rate with constant $\max_{p' \in P} \alpha_{p'}$.
\end{enumerate}
We view both parts as relatively surprising.
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ have only a finite number of full-dimensional level sets.
In other words, although the prediction space $\reals^d$ is infinite, one can pick out just a finite set of prediction points that can act as minimizers of expected loss.

>>>>

\section{Upper bound: polyhedral surrogates}
In this section, we develop the proof of Theorem \ref{thm:main-upper}.
At a high level, the proof has two parts:
\begin{enumerate}
  \item Fix $p \in \simplex$.
        Prove that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for some constant $\alpha_p$.
  \item Apply this result to a carefully chosen finite subset of $\simplex$. Argue that the maximum over the $\alpha_p$'s in this finite set gives the constant factor for the transfer rate.
\end{enumerate}
We view both parts as relatively surprising.
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma$ cover the whole simplex with a finite number of polyhedral level sets.
In other words, although the prediction space $\reals^d$ is infinite, one can pick out just a finite set of prediction points that can act as minimizers of expected loss.
